Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-02-27 eg6-letters/incoherent/incoherent_prl.tex
cleanup abstract

\date{\today}
\begin{abstract}
In the past two decades, deeply virtual Compton scattering of electrons has been successfully 
used to advance our knowledge of the partonic structure of the free proton and investigate 
correlations between the transverse position and the longitudinal momentum of quarks inside 
the nucleon. In this work, we report the first beam spin asymmetry (BSA) measurement of deeply 
virtual Compton scattering (DVCS) off a proton bound in $^4$He. The structure of the bound 
nucleons in nuclei has been studied in inclusive deep-inelastic lepton scattering experiments 
off nuclear targets only, showing a significant difference in longitudinal momentum distribution 
of quarks inside the bound nucleon, known as the EMC effect and still eluding our understanding. 
The data used here were accumulated using a $6$ GeV longitudinally polarized electron beam 
incident on a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B 
at the Thomas Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence 
of the BSA was studied in a wide range of virtual photon and scattered proton kinematics. The 
Q$^2$, x$_B$, and t dependencies of the BSA on the bound proton are compared with those on the 
free proton. In the whole kinematical region of our measurements, the BSA on the bound proton 
is smaller by 20\% to 40\%, indicating possible medium modification of its partonic structure.
\end{abstract}
%\pacs{Valid PACS appear here}

>>>>

\date{\today}
\begin{abstract}
In the past two decades, deeply virtual Compton scattering of electrons has been successfully 
used to advance our knowledge of the partonic structure of the free proton and investigate 
correlations between the transverse position and the longitudinal momentum of quarks inside 
the nucleon.  The structure of bound nucleons in nuclei has only been studied in inclusive
deep-inelastic lepton scattering experiments off nuclear targets, showing a significant
difference in longitudinal momentum distribution of quarks inside the bound nucleon, known as
the EMC effect.  In this work, we report the first beam spin asymmetry (BSA) measurement of
exclusive deeply virtual Compton scattering (DVCS) off a proton bound in $^4$He.  The data
used here were accumulated using a $6$ GeV longitudinally polarized electron beamincident on
a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B at the Thomas
Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence of the BSA was
studied in a wide range of virtual photon and scattered proton kinematics. The Q$^2$, x$_B$,
and t dependencies of the BSA on the bound proton are compared with those on the free proton.
In the whole kinematical region of our measurements, the BSA on the bound proton is smaller by
20\% to 40\%, indicating possible medium modification of its partonic structure.
\end{abstract}
%\pacs{Valid PACS appear here}
